Figures

### 2021-07-02 inst/manuscript/figures.Rmd
Manuscript and SI revised through Results (map accuracy section).

@@

### Figure S4: PlanetScope image density
The density of imagery available for download from the image catalog.

@@

### Figure S5: Initial training site distribution
Figure showing distribution of initial 500 samples per cluster, as well as distribution of points per iteration.  
```{r trainingsites, eval=FALSE}
data("train_val_sites")

@@

### Figure S6: Label count and quality
```{r labelquality, eval=FALSE}
data("label_summary")

@@

### Figures S7 and S8: Consensus label (Bayesian) risk

@@

### Figure S9: Random versus active sampling
```{r, eval=FALSE}
data("iteration_metrics")

@@

### Figure S10: Training data error impact on probability images
```{r, eval = FALSE}
probpal <- viridis::viridis
cprob <- raster(here::here("external/prob/image_c294_r532.tif"))
hprob <- raster(here::here("external/prob/image_c294_r532_high.tif"))
lprob <- raster(here::here("external/prob/image_c294_r532_low.tif"))

@@

### Figure S11: AOI Zones

>>>>

### Figure S4: AOI Zones

@@

### Figure S5: PlanetScope image density
The density of imagery available for download from the image catalog.

@@

### Figure S6: Initial training site distribution
Figure showing distribution of initial 500 samples per cluster, as well as distribution of points per iteration.  
```{r trainingsites, eval=FALSE}
data("train_val_sites")

@@

### Figure S7: Label count and quality
```{r labelquality, eval=FALSE}
data("label_summary")

@@

### Figures S8 and S9: Consensus label (Bayesian) risk

@@

### Figure S10: Random versus active sampling
```{r, eval=FALSE}
data("iteration_metrics")

@@

### Figure S11: Training data error impact on probability images
```{r, eval = FALSE}
probpal <- viridis::viridis
cprob <- raster(here::here("external/prob/image_c294_r532.tif"))
hprob <- raster(here::here("external/prob/image_c294_r532_high.tif"))
lprob <- raster(here::here("external/prob/image_c294_r532_low.tif"))

@@
